Dynamics Analysis: The Sound of Teaching Music 1

### 2020-07-29 script/RNotebook/additional240720/dynamics.Rmd
upload analysis with new trimmed
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a summary of all analyses for dynamics.

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_dyn_order_group_all)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_acc_dyn_order_group_all)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_art_order_group_all)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_acc_art_order_group_all)

@@

```{r file, include = FALSE}
filename_vel = "../R/trimmed/data_vel.csv"
filename_vel_acc = "../R/trimmed/data_vel_acc.csv"
```

@@

```{r vel_dyn_all, echo = FALSE}
# Group mean
vel_dyn_all <- aggregate(Mean~Condition*Skill*Subcomponent, data = vel_dyn,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_dyn_all <- cbind(vel_dyn_all[,1:3], as.data.frame(vel_dyn_all[,4]))
# Change colnames
colnames(vel_dyn_all) <- c("Condition", "Skill", "Subcomponent", "N", "Mean", "SD", "SEM")
print(vel_dyn_all)
```

@@

#### Box plot
```{r vel_dyn_all_box, echo = FALSE}
p_vel_dyn_all_box <- ggplot(data = vel_dyn, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(0.75)) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics")
p_vel_dyn_all_box
```

### Statistics
#### Normality check
```{r normality1, echo = FALSE}
# Reduce unused factors
vel_dyn$Subcomponent <- factor(vel_dyn$Subcomponent)
vel_dyn_norm <- by(vel_dyn$Mean, list(vel_dyn$Condition, vel_dyn$Subcomponent), shapiro.test)
print(vel_dyn_norm)
```

#### Two-way ANOVA (ez)
```{r stats1, echo = FALSE}
vel_dyn_aov <- ezANOVA(
  data = df_vel_dyn
  , dv = .(Velocity)
  , wid = .(SubNr)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_dyn_aov$ANOVA$F <- round(vel_dyn_aov$ANOVA$F, 4)
vel_dyn_aov$ANOVA$p <- round(vel_dyn_aov$ANOVA$p, 4)
print(vel_dyn_aov$ANOVA)
```

@@

```{r vel_acc_dyn_all, echo = FALSE}
# Group mean
vel_acc_dyn_all <- aggregate(Mean~Condition*Skill*Subcomponent, data = vel_acc_dyn,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_acc_dyn_all <- cbind(vel_acc_dyn_all[,1:3], as.data.frame(vel_acc_dyn_all[,4]))
# Change colnames
colnames(vel_acc_dyn_all) <- c("Condition", "Skill", "Subcomponent", "N", "Mean", "SD", "SEM")
print(vel_acc_dyn_all)
```

@@

#### Box plot
```{r vel_acc_dyn_all_box, echo = FALSE}
p_vel_acc_dyn_all_box <- ggplot(data = vel_acc_dyn, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(0.75)) +
  labs(y = "Difference", subtitle = "KV-Diff: Dynamics")
p_vel_acc_dyn_all_box
```

### Statistics
#### Normality check
```{r normality2, echo = FALSE}
# Reduce unused factors
vel_acc_dyn$Subcomponent <- factor(vel_acc_dyn$Subcomponent)
vel_acc_dyn_norm <- by(vel_acc_dyn$Mean, list(vel_acc_dyn$Condition, vel_acc_dyn$Subcomponent), shapiro.test)
print(vel_acc_dyn_norm)
```

#### Two-way ANOVA (ez)
```{r stats3, echo = FALSE}
vel_acc_dyn_aov <- ezANOVA(
  data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF")
  , dv = .(Acc)
  , wid = .(SubNr)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_acc_dyn_aov$ANOVA$F <- round(vel_acc_dyn_aov$ANOVA$F, 4)
vel_acc_dyn_aov$ANOVA$p <- round(vel_acc_dyn_aov$ANOVA$p, 4)
print(vel_acc_dyn_aov$ANOVA)
```

@@

# KV-Order-Dynamics
- Investigate whether there is any order effect of the conditions.

## 1. All{#vel_dyn_order_group_all}
```{r vel_dyn_order_all, echo = all}
# For each participant
vel_dyn_order <- aggregate(Velocity~SubNr*Condition*Skill*Subcomponent*Order, data = df_vel_dyn,
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_dyn_order <- cbind(vel_dyn_order[,1:5], as.data.frame(vel_dyn_order[,6]))
# Change colnames
colnames(vel_dyn_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_dyn_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_dyn_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_dyn_order_all <- cbind(vel_dyn_order_all[,1:4], as.data.frame(vel_dyn_order_all[,5]))
# Change colnames
colnames(vel_dyn_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_dyn_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_dyn_order_all_bar, echo = FALSE}
p_vel_dyn_order_all <- ggplot(data = vel_dyn_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") + coord_cartesian(ylim = c(40, 100))
p_vel_dyn_order_all
```

#### Box plot
```{r vel_dyn_order_all_box, echo = FALSE}
p_vel_dyn_order_all_box <- ggplot(data = vel_dyn_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") 
p_vel_dyn_order_all_box
```

### Statistics
#### Normality check
```{r normality5, echo = FALSE}
# Normality check
vel_dyn_order$Subcomponent <- factor(vel_dyn_order$Subcomponent)
vel_dyn_order_norm <- by(vel_dyn_order$Mean, list(vel_dyn_order$Condition, vel_dyn_order$Subcomponent, vel_dyn_order$Order), shapiro.test)
print(vel_dyn_order_norm)
```

#### Three-way ANOVA (ez)
```{r stats9, echo = FALSE}
vel_dyn_order_aov <- ezANOVA(
  data = df_vel_dyn
  , dv = .(Velocity)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_dyn_order_aov$ANOVA$F <- round(vel_dyn_order_aov$ANOVA$F, 4)
vel_dyn_order_aov$ANOVA$p <- round(vel_dyn_order_aov$ANOVA$p, 4)
print(vel_dyn_order_aov)
```

# KV-Diff-Order-Dynamics
- Investigate whether there is any order effect of the conditions.

## 1. All{#vel_acc_dyn_order_group_all}
```{r vel_acc_dyn_order_all, echo = all}
# For each participant
vel_acc_dyn_order <- aggregate(Acc~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF"),
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_acc_dyn_order <- cbind(vel_acc_dyn_order[,1:5], as.data.frame(vel_acc_dyn_order[,6]))
# Change colnames
colnames(vel_acc_dyn_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_acc_dyn_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_acc_dyn_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_acc_dyn_order_all <- cbind(vel_acc_dyn_order_all[,1:4], as.data.frame(vel_acc_dyn_order_all[,5]))
# Change colnames
colnames(vel_acc_dyn_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_acc_dyn_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_acc_dyn_order_all_bar, echo = FALSE}
p_vel_acc_dyn_order_all <- ggplot(data = vel_acc_dyn_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "Difference", subtitle = "KV-Diff: Dynamics")
p_vel_acc_dyn_order_all
```

#### Box plot
```{r vel_acc_dyn_order_all_box, echo = FALSE}
p_vel_acc_dyn_order_all_box <- ggplot(data = vel_acc_dyn_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "Difference", subtitle = "KV-Diff: Dynamics") 
p_vel_acc_dyn_order_all_box
```

### Statistics
#### Normality check
```{r normality6, echo = FALSE}
# Normality check
vel_acc_dyn_order$Subcomponent <- factor(vel_acc_dyn_order$Subcomponent)
vel_acc_dyn_order_norm <- by(vel_acc_dyn_order$Mean, list(vel_acc_dyn_order$Condition, vel_acc_dyn_order$Subcomponent, vel_acc_dyn_order$Order), shapiro.test)
print(vel_acc_dyn_order_norm)
```

#### Three-way ANOVA (ez)
```{r stats10, echo = FALSE}
vel_acc_dyn_order_aov <- ezANOVA(
  data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF")
  , dv = .(Acc)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_acc_dyn_order_aov$ANOVA$F <- round(vel_acc_dyn_order_aov$ANOVA$F, 4)
vel_acc_dyn_order_aov$ANOVA$p <- round(vel_acc_dyn_order_aov$ANOVA$p, 4)
print(vel_acc_dyn_order_aov)
```

# KV-Order-Articulation
- Investigate whether there is any order effect of the conditions.

## 1. All{#vel_art_order_group_all}
```{r vel_art_order_all, echo = all}
# For each participant
vel_art_order <- aggregate(Velocity~SubNr*Condition*Skill*Subcomponent*Order, data = df_vel_art,
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_art_order <- cbind(vel_art_order[,1:5], as.data.frame(vel_art_order[,6]))
# Change colnames
colnames(vel_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_art_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_art_order_all <- cbind(vel_art_order_all[,1:4], as.data.frame(vel_art_order_all[,5]))
# Change colnames
colnames(vel_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_art_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_art_order_all_bar, echo = FALSE}
p_vel_art_order_all <- ggplot(data = vel_art_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Articulation") + coord_cartesian(ylim = c(40, 100))
p_vel_art_order_all
```

#### Box plot
```{r vel_art_order_all_box, echo = FALSE}
p_vel_art_order_all_box <- ggplot(data = vel_art_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Articulation") 
p_vel_art_order_all_box
```

### Statistics
#### Normality check
```{r normality7, echo = FALSE}
# Normality check
vel_art_order$Subcomponent <- factor(vel_art_order$Subcomponent)
vel_art_order_norm <- by(vel_art_order$Mean, list(vel_art_order$Condition, vel_art_order$Subcomponent, vel_art_order$Order), shapiro.test)
print(vel_art_order_norm)
```

#### Three-way ANOVA (ez)
```{r stats11, echo = FALSE}
vel_art_order_aov <- ezANOVA(
  data = df_vel_art
  , dv = .(Velocity)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_art_order_aov$ANOVA$F <- round(vel_art_order_aov$ANOVA$F, 4)
vel_art_order_aov$ANOVA$p <- round(vel_art_order_aov$ANOVA$p, 4)
print(vel_art_order_aov)
```

# KV-Diff-Order-Articulation
- Investigate whether there is any order effect of the conditions.

## 1. All{#vel_acc_art_order_group_all}
```{r vel_acc_art_order_all, echo = all}
# For each participant
vel_acc_art_order <- aggregate(Acc~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_vel_acc_art, df_vel_acc_art$Subcomponent == "LtoS" | df_vel_acc_art$Subcomponent == "StoL"),
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_acc_art_order <- cbind(vel_acc_art_order[,1:5], as.data.frame(vel_acc_art_order[,6]))
# Change colnames
colnames(vel_acc_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_acc_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_acc_art_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_acc_art_order_all <- cbind(vel_acc_art_order_all[,1:4], as.data.frame(vel_acc_art_order_all[,5]))
# Change colnames
colnames(vel_acc_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_acc_art_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

>>>>

Description: This is a summary of all analyses for dynamics. **Add excluded 14 participants.**

@@

<!-- - Order analysis (teaching/performing first?) -->
<!--   + [All](#vel_dyn_order_group_all) -->

@@

<!-- - Order analysis (teaching/performing first?) -->
<!--   + [All](#vel_acc_dyn_order_group_all) -->

@@

<!-- - Order analysis (teaching/performing first?) -->
<!--   + [All](#vel_art_order_group_all) -->

@@

<!-- - Order analysis (teaching/performing first?) -->
<!--   + [All](#vel_acc_art_order_group_all) -->

@@

```{r file, include = FALSE}
filename_vel = "./trimmed/data_vel.csv"
filename_vel_acc = "./trimmed/data_vel_acc.csv"
```

@@

```{r vel_dyn_all, echo = FALSE}
# Group mean
vel_dyn_all <- aggregate(Mean~Condition*Skill*Subcomponent, data = subset(vel_dyn, vel_dyn$SubNr != 3 & vel_dyn$SubNr != 14), # exclude SubNr 3 & 14 as one of the conditions is completely missing
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_dyn_all <- cbind(vel_dyn_all[,1:3], as.data.frame(vel_dyn_all[,4]))
# Change colnames
colnames(vel_dyn_all) <- c("Condition", "Skill", "Subcomponent", "N", "Mean", "SD", "SEM")
print(vel_dyn_all)
```

@@

#### Box plot
```{r vel_dyn_all_box, echo = FALSE}
p_vel_dyn_all_box <- ggplot(data = subset(vel_dyn, vel_dyn$SubNr != 3 & vel_dyn$SubNr != 14), aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(0.75)) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics")
p_vel_dyn_all_box
```

### Statistics
#### Normality check
```{r normality1, echo = FALSE}
# exclude SubNr 3 & 14
vel_dyn <- subset(vel_dyn, vel_dyn$SubNr != 3 & vel_dyn$SubNr != 14)
# Reduce unused factors
vel_dyn$Subcomponent <- factor(vel_dyn$Subcomponent)
vel_dyn_norm <- by(vel_dyn$Mean, list(vel_dyn$Condition, vel_dyn$Subcomponent), shapiro.test)
print(vel_dyn_norm)
```

#### Two-way ANOVA (ez)
```{r stats1, echo = FALSE}
vel_dyn_aov <- ezANOVA(
  data = subset(df_vel_dyn, df_vel_dyn$SubNr != 3 & df_vel_dyn$SubNr != 14)
  , dv = .(Velocity)
  , wid = .(SubNr)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_dyn_aov$ANOVA$F <- round(vel_dyn_aov$ANOVA$F, 4)
vel_dyn_aov$ANOVA$p <- round(vel_dyn_aov$ANOVA$p, 4)
print(vel_dyn_aov$ANOVA)
```

@@

```{r vel_acc_dyn_all, echo = FALSE}
# Group mean
vel_acc_dyn_all <- aggregate(Mean~Condition*Skill*Subcomponent, data = subset(vel_acc_dyn, vel_acc_dyn$SubNr != 3 & vel_acc_dyn$SubNr != 14), # exclude SubNr 3 & 14 as one of the conditions is completely missing
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_acc_dyn_all <- cbind(vel_acc_dyn_all[,1:3], as.data.frame(vel_acc_dyn_all[,4]))
# Change colnames
colnames(vel_acc_dyn_all) <- c("Condition", "Skill", "Subcomponent", "N", "Mean", "SD", "SEM")
print(vel_acc_dyn_all)
```

@@

#### Box plot
```{r vel_acc_dyn_all_box, echo = FALSE}
p_vel_acc_dyn_all_box <- ggplot(data = subset(vel_acc_dyn, vel_acc_dyn$SubNr != 3 & vel_acc_dyn$SubNr != 14), aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(0.75)) +
  labs(y = "Difference", subtitle = "KV-Diff: Dynamics")
p_vel_acc_dyn_all_box
```

### Statistics
#### Normality check
```{r normality2, echo = FALSE}
# exclude SubNr 3 & 14
vel_acc_dyn <- subset(vel_acc_dyn, vel_acc_dyn$SubNr != 3 & vel_acc_dyn$SubNr != 14)
# Reduce unused factors
vel_acc_dyn$Subcomponent <- factor(vel_acc_dyn$Subcomponent)
vel_acc_dyn_norm <- by(vel_acc_dyn$Mean, list(vel_acc_dyn$Condition, vel_acc_dyn$Subcomponent), shapiro.test)
print(vel_acc_dyn_norm)
```

#### Two-way ANOVA (ez)
```{r stats3, echo = FALSE}
df_vel_acc_dyn_exc <- subset(df_vel_acc_dyn, df_vel_acc_dyn$SubNr != 3 & df_vel_acc_dyn$SubNr != 14)
vel_acc_dyn_aov <- ezANOVA(
  data = subset(df_vel_acc_dyn_exc, df_vel_acc_dyn_exc$Subcomponent == "FtoP" | df_vel_acc_dyn_exc$Subcomponent == "PtoF")
  , dv = .(Acc)
  , wid = .(SubNr)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_acc_dyn_aov$ANOVA$F <- round(vel_acc_dyn_aov$ANOVA$F, 4)
vel_acc_dyn_aov$ANOVA$p <- round(vel_acc_dyn_aov$ANOVA$p, 4)
print(vel_acc_dyn_aov$ANOVA)
```

@@

<!-- # KV-Order-Dynamics -->
<!-- - Investigate whether there is any order effect of the conditions. -->

<!-- ## 1. All{#vel_dyn_order_group_all} -->
<!-- ```{r vel_dyn_order_all, echo = all} -->
<!-- # For each participant -->
<!-- vel_dyn_order <- aggregate(Velocity~SubNr*Condition*Skill*Subcomponent*Order, data = df_vel_dyn, -->
<!--                                FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))}) -->
<!-- vel_dyn_order <- cbind(vel_dyn_order[,1:5], as.data.frame(vel_dyn_order[,6])) -->
<!-- # Change colnames -->
<!-- colnames(vel_dyn_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD") -->

<!-- # Group mean -->
<!-- vel_dyn_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_dyn_order, -->
<!--                          FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)}) -->
<!-- vel_dyn_order_all <- cbind(vel_dyn_order_all[,1:4], as.data.frame(vel_dyn_order_all[,5])) -->
<!-- # Change colnames -->
<!-- colnames(vel_dyn_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM") -->
<!-- print(vel_dyn_order_all) -->
<!-- ``` -->

<!-- ### Plot -->
<!-- #### Bar graph -->
<!-- - Error bars show SEM of the mean -->

<!-- ```{r vel_dyn_order_all_bar, echo = FALSE} -->
<!-- p_vel_dyn_order_all <- ggplot(data = vel_dyn_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_bar(stat = "identity", position = position_dodge()) + -->
<!--   geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM), -->
<!--                 width = .2, position = position_dodge(.9)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "KV (0-127)", subtitle = "KV: Dynamics") + coord_cartesian(ylim = c(40, 100)) -->
<!-- p_vel_dyn_order_all -->
<!-- ``` -->

<!-- #### Box plot -->
<!-- ```{r vel_dyn_order_all_box, echo = FALSE} -->
<!-- p_vel_dyn_order_all_box <- ggplot(data = vel_dyn_order, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_boxplot() + -->
<!--   geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "KV (0-127)", subtitle = "KV: Dynamics")  -->
<!-- p_vel_dyn_order_all_box -->
<!-- ``` -->

<!-- ### Statistics -->
<!-- #### Normality check -->
<!-- ```{r normality5, echo = FALSE} -->
<!-- # Normality check -->
<!-- vel_dyn_order$Subcomponent <- factor(vel_dyn_order$Subcomponent) -->
<!-- vel_dyn_order_norm <- by(vel_dyn_order$Mean, list(vel_dyn_order$Condition, vel_dyn_order$Subcomponent, vel_dyn_order$Order), shapiro.test) -->
<!-- print(vel_dyn_order_norm) -->
<!-- ``` -->

<!-- #### Three-way ANOVA (ez) -->
<!-- ```{r stats9, echo = FALSE} -->
<!-- vel_dyn_order_aov <- ezANOVA( -->
<!--   data = df_vel_dyn -->
<!--   , dv = .(Velocity) -->
<!--   , wid = .(SubNr) -->
<!--   , between = .(Order) -->
<!--   , within = .(Condition, Subcomponent) -->
<!--   , type = 3 -->
<!--   , detailed = TRUE -->
<!-- ) -->
<!-- vel_dyn_order_aov$ANOVA$F <- round(vel_dyn_order_aov$ANOVA$F, 4) -->
<!-- vel_dyn_order_aov$ANOVA$p <- round(vel_dyn_order_aov$ANOVA$p, 4) -->
<!-- print(vel_dyn_order_aov) -->
<!-- ``` -->

<!-- # KV-Diff-Order-Dynamics -->
<!-- - Investigate whether there is any order effect of the conditions. -->

<!-- ## 1. All{#vel_acc_dyn_order_group_all} -->
<!-- ```{r vel_acc_dyn_order_all, echo = all} -->
<!-- # For each participant -->
<!-- vel_acc_dyn_order <- aggregate(Acc~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF"), -->
<!--                                FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))}) -->
<!-- vel_acc_dyn_order <- cbind(vel_acc_dyn_order[,1:5], as.data.frame(vel_acc_dyn_order[,6])) -->
<!-- # Change colnames -->
<!-- colnames(vel_acc_dyn_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD") -->

<!-- # Group mean -->
<!-- vel_acc_dyn_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_acc_dyn_order, -->
<!--                          FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)}) -->
<!-- vel_acc_dyn_order_all <- cbind(vel_acc_dyn_order_all[,1:4], as.data.frame(vel_acc_dyn_order_all[,5])) -->
<!-- # Change colnames -->
<!-- colnames(vel_acc_dyn_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM") -->
<!-- print(vel_acc_dyn_order_all) -->
<!-- ``` -->

<!-- ### Plot -->
<!-- #### Bar graph -->
<!-- - Error bars show SEM of the mean -->

<!-- ```{r vel_acc_dyn_order_all_bar, echo = FALSE} -->
<!-- p_vel_acc_dyn_order_all <- ggplot(data = vel_acc_dyn_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_bar(stat = "identity", position = position_dodge()) + -->
<!--   geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM), -->
<!--                 width = .2, position = position_dodge(.9)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "Difference", subtitle = "KV-Diff: Dynamics") -->
<!-- p_vel_acc_dyn_order_all -->
<!-- ``` -->

<!-- #### Box plot -->
<!-- ```{r vel_acc_dyn_order_all_box, echo = FALSE} -->
<!-- p_vel_acc_dyn_order_all_box <- ggplot(data = vel_acc_dyn_order, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_boxplot() + -->
<!--   geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "Difference", subtitle = "KV-Diff: Dynamics")  -->
<!-- p_vel_acc_dyn_order_all_box -->
<!-- ``` -->

<!-- ### Statistics -->
<!-- #### Normality check -->
<!-- ```{r normality6, echo = FALSE} -->
<!-- # Normality check -->
<!-- vel_acc_dyn_order$Subcomponent <- factor(vel_acc_dyn_order$Subcomponent) -->
<!-- vel_acc_dyn_order_norm <- by(vel_acc_dyn_order$Mean, list(vel_acc_dyn_order$Condition, vel_acc_dyn_order$Subcomponent, vel_acc_dyn_order$Order), shapiro.test) -->
<!-- print(vel_acc_dyn_order_norm) -->
<!-- ``` -->

<!-- #### Three-way ANOVA (ez) -->
<!-- ```{r stats10, echo = FALSE} -->
<!-- vel_acc_dyn_order_aov <- ezANOVA( -->
<!--   data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF") -->
<!--   , dv = .(Acc) -->
<!--   , wid = .(SubNr) -->
<!--   , between = .(Order) -->
<!--   , within = .(Condition, Subcomponent) -->
<!--   , type = 3 -->
<!--   , detailed = TRUE -->
<!-- ) -->
<!-- vel_acc_dyn_order_aov$ANOVA$F <- round(vel_acc_dyn_order_aov$ANOVA$F, 4) -->
<!-- vel_acc_dyn_order_aov$ANOVA$p <- round(vel_acc_dyn_order_aov$ANOVA$p, 4) -->
<!-- print(vel_acc_dyn_order_aov) -->
<!-- ``` -->

<!-- # KV-Order-Articulation -->
<!-- - Investigate whether there is any order effect of the conditions. -->

<!-- ## 1. All{#vel_art_order_group_all} -->
<!-- ```{r vel_art_order_all, echo = all} -->
<!-- # For each participant -->
<!-- vel_art_order <- aggregate(Velocity~SubNr*Condition*Skill*Subcomponent*Order, data = df_vel_art, -->
<!--                                FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))}) -->
<!-- vel_art_order <- cbind(vel_art_order[,1:5], as.data.frame(vel_art_order[,6])) -->
<!-- # Change colnames -->
<!-- colnames(vel_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD") -->

<!-- # Group mean -->
<!-- vel_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_art_order, -->
<!--                          FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)}) -->
<!-- vel_art_order_all <- cbind(vel_art_order_all[,1:4], as.data.frame(vel_art_order_all[,5])) -->
<!-- # Change colnames -->
<!-- colnames(vel_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM") -->
<!-- print(vel_art_order_all) -->
<!-- ``` -->

<!-- ### Plot -->
<!-- #### Bar graph -->
<!-- - Error bars show SEM of the mean -->

<!-- ```{r vel_art_order_all_bar, echo = FALSE} -->
<!-- p_vel_art_order_all <- ggplot(data = vel_art_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_bar(stat = "identity", position = position_dodge()) + -->
<!--   geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM), -->
<!--                 width = .2, position = position_dodge(.9)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "KV (0-127)", subtitle = "KV: Articulation") + coord_cartesian(ylim = c(40, 100)) -->
<!-- p_vel_art_order_all -->
<!-- ``` -->

<!-- #### Box plot -->
<!-- ```{r vel_art_order_all_box, echo = FALSE} -->
<!-- p_vel_art_order_all_box <- ggplot(data = vel_art_order, aes(x = Subcomponent, y = Mean, fill = Condition)) + -->
<!--   geom_boxplot() + -->
<!--   geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) + -->
<!--   facet_wrap(Order ~ .) + -->
<!--   labs(y = "KV (0-127)", subtitle = "KV: Articulation")  -->
<!-- p_vel_art_order_all_box -->
<!-- ``` -->

<!-- ### Statistics -->
<!-- #### Normality check -->
<!-- ```{r normality7, echo = FALSE} -->
<!-- # Normality check -->
<!-- vel_art_order$Subcomponent <- factor(vel_art_order$Subcomponent) -->
<!-- vel_art_order_norm <- by(vel_art_order$Mean, list(vel_art_order$Condition, vel_art_order$Subcomponent, vel_art_order$Order), shapiro.test) -->
<!-- print(vel_art_order_norm) -->
<!-- ``` -->
